% resume-a4.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2010 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[a4paper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage[utf8]{inputenc}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0mm}

% Adjust margins to 12.5mm on all sides
\addtolength{\oddsidemargin}{-12.5mm}
\addtolength{\evensidemargin}{-12.5mm}
\addtolength{\textwidth}{25mm}
\addtolength{\topmargin}{-12.5mm}
\addtolength{\textheight}{25mm}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}

\newcommand{\resheading}[1]{{\vspace{5mm}\Large
    \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1
            \vphantom{p\^{E}}}}\end{minipage}}}}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{172mm}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{center}
\textbf{\huge CV - Peter Mechlenborg}\\
\end{center}
\vspace{1.0cm}

\begin{tabular*}{180mm}{l@{\extracolsep{\fill}}r}
\textbf{\large Peter J. M. Mechlenborg}  & phone: +45 2242 5356\\

Multebærvej 33 & peter.mechlenborg@gmail.com\\
8600, Silkeborg\\
Denmark\\\\
\end{tabular*}
\\

\vspace{0.25mm}

\resheading{Work Experience}
\begin{itemize}
\item \ressubheading{Trifork A/S}{Aarhus, DK}{Software Developer}{April 2012 - Present}
  \begin{itemize}

    \resitem{Design and implementation in the back-end team for the
      National Danish Medicine Card.  Focus on Java enterprise
      development and Riak development and data modeling.}

  \end{itemize}

\item \ressubheading{Actua ApS}{Aarhus, DK}{Software Developer, Consultant}{Oct 2008 - Marts 2012}
  \begin{itemize}

    \resitem{Design, implementation, and analysis on top of a data
      warehouse system for a wireless broadband operator.}

    \resitem{Documentation and proof-of-concept implementation of an
      architecture for secure communication between distributed energy
      resources.  The project was conducted under ForskEL (see also
      www.second1.dk).}

    \resitem{Canvas sale on a internal project to relaunch a product
      for rapid near-infrared spectroscopy inside production lines.}

    \resitem{Design and implementation of a Nagios based server and
      network monitoring system for a wireless broadband operator.}

  \end{itemize}

\item  \ressubheading{Mu ApS}{Aarhus, DK}{Software Developer and Team lead}{Jan 2007 - Sep 2008}

  \begin{itemize}

    \resitem{Tech. lead on the back-end of an algorithmic trading
      system.  The system was being developed for a London based
      customer in the financial sector.}

    \resitem{Team lead on the new Aarhus office, responsible for
      communication and coordination between Aarhus and Copenhagen.}

  \end{itemize}

\item  \ressubheading{Mu ApS}{Copenhagen, DK}{Software Developer}{May 2006 - jan 2007}

  \begin{itemize}

    \resitem{Software developer on an algorithmic trading system.
      Developed for a London based customer in the financial sector.}

    \resitem{Software developer on an algorithmic trading system for
      on-line betting.}

  \end{itemize}

\item  \ressubheading{DAIMI, CPN group}{Aarhus, DK}{Student Programmer}{2004 - 2005}

  \begin{itemize}

    \resitem{Back-end programmer on CPN-Tools (IDE for Coloured Petri
      Nets).}

  \end{itemize}

\end{itemize}

\pagebreak

\resheading{Education}
\begin{itemize}
\item \ressubheading{DAIMI, University of Aarhus}{}{Master's degree in
  Computer Science}{Sep. 1999 - April. 2006}
	\begin{itemize}
	  \resitem{Master Thesis: Language Interoperability on Object-Oriented Virtual Machines}
	\end{itemize}

\item \ressubheading{Internship, University of Bordeaux}{}{Programming
  language group under Charles Consel}{3 months in 2005}
	\begin{itemize}
	  \resitem{Part of a project to develop a domain specific
            language for controlling tele-communication using the
            Session Initiation Protocol (SIP)}
	\end{itemize}


\end{itemize}

\resheading{Skills}

\begin{description}
\item[Languages:] Erlang, Java, JavaScript, Python, PostgreSQL, Common
  Lisp, R, SML, OCaml, C, and Scheme.  (Listed after decreasing
  experience).
\item[Operating Systems:] Linux, Solaris.
\item[Protocols:] X.509 Certificates, SNMP, TCP/IP.
\item[Project Management:] Some experience with agile teams of 1 to 4
  persons.
\item[Methodology:] Scrum, Kanban, Lean.
\item[Miscellaneous:] Short term experience with canvas sale.
\end{description}

\resheading{Certifications}
\begin{itemize}
\item
	\ressubheading{Scrum Master}{Stora Nyteboda, SE}{5 days at Camp Scrum (http://campscrum.com)}{Oct. 2007}

\end{itemize}

\resheading{Publications and Presentations}
\begin{description}
\item["Flexible Language Interoperability",] \emph{The Journal of
  Object Technology}, Volume 6, no. 8, Sep. 2007

\item[Erlang,] presented a talk on Erlang at
  \emph{Softwareudviking-på-tværs, Teknologisk Institut,} in Dec. 2007
  as well as in various cities around Denmark for IDA (www.ida.dk).

\end{description}

\resheading{Hobbies and Interests}

\begin{itemize}
\item Handball - since I was a teenager and for a couple of years
  semi-professional.
\item Kayaking - started a couple of years ago.
\item Running - on/off my whole life.
\item Computer gaming - since i was a teenager.
\item Reading fantasy novels - from the 10th grade and still...
\end{itemize}

\end{document}

